---
title: "pediRES-Q CPR Report Card"
author: ""
date: ""
header-includes:
  - \usepackage{floatrow}
output: 
  pdf_document:
   keep_tex: true
params:
  DepthPlot: "NULL"
  RatePlot: "NULL"
  CCFTbl: "NULL"
  CCFPie: "NULL"
  AvgDepthRate: "NULL"
  PercTbl: "NULL"
  
  
---

```{r, include=FALSE}
library(knitr)
library(kableExtra)
```

\newfloatcommand{btabbox}{table}

\begin{figure}[H]
  \begin{floatrow}
    \ffigbox{%
```{r, fig.align = "right", echo = F, fig.height=3, fig.align='center'}
params[["CCFPie"]]
```
    }{\caption{CCF Pie Chart}}

    \btabbox{%
```{r, fig.align = "right", echo = F}
knitr::kable(params[["CCFTbl"]], format = "latex")
```
    }{\caption{CCF Table}}
  \end{floatrow}
\end{figure}

\begin{figure}[H]
  \begin{floatrow}
    \btabbox{%
```{r, fig.align = "right", echo = F}
knitr::kable(params[["AvgDepthRate"]], format = "latex")
```
    }{\caption{Average Table}}
    
     \btabbox{%
```{r, fig.align = "right", echo = F}
knitr::kable(params[["PercTbl"]], format = "latex")
```
   }{\caption{Percent Table}}
  \end{floatrow}
\end{figure}

Please note that the CCF calculations for this report **do not** take into account periods of intermittent ROSC. This is a hard chest compression fraction calculation defined exclusively by time in compressions over the total time of the event.

```{r depth plot, echo = FALSE, fig.width=15, fig.height=8, warning=FALSE}
params[["DepthPlot"]]
```

```{r rate plot, echo = FALSE, fig.width=15, fig.height=8, warning=FALSE}
params[["RatePlot"]]
```

* A filter has been applied to remove all compression depths registering <0.4cm or >10cm and all compression rates registering <50cpm or >180cpm. 