---
title: "CPR Report Card"
author: ""
date: ""
output: 
  html_document
params:
  DepthPlot: "NULL"
  RatePlot: "NULL"
  CCFTbl: "NULL"
  CCFPie: "NULL"
  AvgDepthRate: "NULL"
  
  
  
---
## Table 1: Average Depth and Rate for Event

```{r Avg Depth Rate Table, echo = FALSE, fig.align='left'}
# knitr::kable(list(params[["CCFtbl"]], params[["AvgDepthRate"]])) 
params[["AvgDepthRate"]]
```

## Table 2: CCF Metrics for Event

```{r CCF Table, echo = FALSE, fig.align='left'}
params[["CCFTbl"]]
```

# Figure 1: CCF Pie Chart

```{r CCF Pit, echo = FALSE, fig.align='right'}
params[["CCFPie"]]
```

## Figure 2: Depth Summary

The plot below shows depth markers for each compression registered over the course of the event overlaid by target guidelines appropriate for the selected age group.

```{r depth plot, echo = FALSE}
params[["DepthPlot"]]
```

# Figure 3: Depth Summary

The plot below shows rate markers for each compression registered over the course of the event overlaid by target guidelines.

```{r rate plot, echo = FALSE}
params[["RatePlot"]]
```